---
title: "Data_Science_EA4_Marco_Krömer"
author: "Marco_Krömer"
date: "2024-05-10"
output: html_document
---

## Setup

Import the data("iris")
```{r setup}
knitr::opts_chunk$set(echo = TRUE)
library(datasets)
library(ggplot2)
data(iris)
```

## Scatter plot

Make a scatter plot with x-axis: Sepal.Length and y-axis: Sepal.Width, and the species should be shown in different colors

```{r}
ggplot(
       data=iris,
       mapping=aes(
                    x=Sepal.Length,
                    y=Sepal.Width,
                    color=Species)
        ) + geom_point()
```

### Regression line

Add regression line for the previous plot with the whole dataset (regardless of the species)

```{r}
ggplot(
      data=iris,
      mapping=aes(
                    x=Sepal.Length,
                    y=Sepal.Width)
      ) + geom_point(aes(color=Species)) + geom_smooth(formula = y ~ x, method="lm")
```

### Pearson correlation

Calculate the Pearson correlation for this plot

```{r}
cor(
      iris$Sepal.Length,
      iris$Sepal.Width,
      method = 'pearson')
```


## Boxplot

Make the boxplot for Petal.Width with 3 species separately in the x-axis in different colors  

```{r}
ggplot(
        data=iris,
        mapping=aes(
                    x=Species, 
                    y=Petal.Width,
                    color=Species)
        )+ geom_boxplot() 
```

## Histogram

Make the histogram for Petal.Width with 3 species separately in x-axis in different colors


```{r}
ggplot(
        data=iris,
        mapping=aes( 
                      x=Petal.Width, 
                      color=Species)
        )+ geom_histogram(bins=30) 
```

## T-test

Run the t-test of Petal.Width between setosa and virginica, and give the conclusion if the width is a statistically significant difference between 2 species
```{r}
t.test(
        Petal.Width ~ Species, 
        iris, 
        Species %in% c("setosa", "virginica")
       )
```
### Conclusion   

The p-value of 2.2e-16 is less than the Alpha level of 0.05
The mean values of the two species are therefore not the same and there is a significant difference in the petal Width of the species


